---
title: "Assignment 5"
author: "Alejandro Osborne"
date: "March 3, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(RMySQL)
library(tidyverse)
library(tidyr)
library(dplyr)
library(tidyselect)
library(ggplot2)
library(stringr)
library(zoo, warn.conflicts = FALSE)
```

##Establishing connection between R and Database
```{r}
loadsql <- dbDriver("MySQL")
openlink = dbConnect(MySQL(), user='root', password ='celeborn', dbname='arrivals', host='localhost')
```

##Query to get Data
```{r}
AirportDataset<-"SELECT * FROM arrivals"
arrivals <-dbGetQuery(openlink, AirportDataset)
dbDisconnect(openlink)
```
##Loading Queried Data into data frame
```{r}
FlightData <- data.frame(arrivals)
FlightData
```
##Initial data is missing labels for 2 rows, will fix with "zoo" Library

```{r}
FlightData$Airline[FlightData$Airline == ""] <- NA
FlightData$Airline <- na.locf(FlightData$Airline, option="locf")
FlightData <- FlightData
FlightData
```
##Finally Tidying the data (Stacking)
```{r}
NewFlightData<-gather(FlightData, "City", "FlightCount", 3:7)
tidied_up <- arrange(NewFlightData, FlightStatus)
tidied_up
```

##Summary Statistics to give us a general overview of what the numbers can vaguely describe to us
```{r}
tidied_up %>% group_by(Airline) %>% filter(FlightStatus == "delayed") %>% summarise(mean = mean(FlightCount), min = min(FlightCount), max = max(FlightCount), median = median(FlightCount), stdev = sd(FlightCount), total = sum(FlightCount))
```
##We seek to find the last bit needed to reach a conclusion of any kind regarding this data. We create a field that describes the ratio of flights delayed/on time to the amount of flights scheduled. 

```{r}
NewTidied <- tidied_up %>% group_by(Airline, City) %>% arrange(Airline) %>% mutate(CityCounts = sum(FlightCount), NewRatio = FlightCount/CityCounts)
NewTidied
```
##Finally we find The rations for the airlines in general (we only look at the Delayed flights) and we can see by a decent margin that AM West has more delayed flights than Alaska.
```{r}
NewTidied %>% group_by(Airline) %>% filter(FlightStatus == "delayed") %>% summarise(mean = mean(NewRatio), min = min(NewRatio), max = max(NewRatio), median = median(NewRatio), standard_deviation = sd(NewRatio))
```


